---
title: "graphs"
author: "Maura Lievano"
date: "4/11/2018"
output:
  pdf_document: default
  html_document: default
---



```{r Load Libraries, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(plyr)
library(dplyr)
library(xtable)
library(base)
library(readr)
library(xts)
library(qdapTools)
library(data.table)
library(tidyr)
library(textshape) # reshaping of categorical variables, which is very cool 
library(tibble) #works df
library(tidyverse)
```


```{r load data, include=FALSE}
load("~/Desktop/sfpd/datasf.RData")
load("~/Desktop/sfpd/cat.RData")
load("~/Desktop/sfpd/time_vars.RData")
load("~/Desktop/sfpd/districts/Larceny.RData")
```

```{r include=FALSE}
data_cat = cbind(time_vars, cat_dow)
data_cat = data_cat[ , -c(8, 48)]
daily_count = colSums(data_cat[, 8:46])
daily_count = data.frame(daily_count)
daily_count = setDT(daily_count, keep.rownames = TRUE)[]
```

```{r format frequency table, include=FALSE}
colnames(daily_count) <- c("Category", "Count")
daily_count = daily_count %>% arrange(desc(Count)) 

```


```{r}
daily_count = format(daily_count, digits = 6)

rownames(daily_count) <- NULL

```

```{r}

write.table(daily_count, file = "daily_count.txt", sep = ",", quote = FALSE, row.names = F)
```

```


```{r}
names_cats = c("Date", "Arson", "Assault","Bad_checks", 
               "Bribery", "Burglary", "Disorderly", 
               "DUI",  "Drugs", "Drunkenness", 
               "Embezzlement", "Extortion", "Family", 
               "Forgery", "Fraud", "Gambling", 
               "Kidnapping", "Larceny", "Liquor", 
               "Loitering", "MissingP", "Non_criminal", 
               "Other", "Pornography", "Prostitution", 
               "Recovered_Veh", "Robbery", "Runaway",               
               "Secondary",  "Sex_force",  "sex_non_force", 
               "Stolen_property", "Suicide", "OCC", 
               "TREA",  "Trespass",  "Vandalism", 
               "Vehicle_theft", "Warrants", "Weapon_laws")  
```



```{r run models and create table, include=FALSE}
data = cbind(time_vars, Larceny)
outcome = Larceny

results <- list()
for (i in seq_along(outcome)) {
  eq <- paste(outcome[i],"~ after + time_r + time2 + tafter + t2after + dow")
  fit <- lm(as.formula(eq), data = data)
  summary <- summary(fit)
  coefficients = summary$coefficients
  results[[i]] <- coefficients[1:2,]
}

estimates = do.call(rbind, lapply(results, data.frame))
rownames(estimates) <- NULL
estimates = estimates[, c(1, 2, 4)]


estimates = cbind(District = 1, estimates)

colnames(estimates) <- c("District", "Estimate", "SE", "p_value")

estimates = round(estimates, digits = 6)

district_names = c("Bayview", "Central", "Ingleside",
                    "Mission", "Northern", "Park",
                    "Richmond", "Southern", "Taraval",
                    "Tenderloin")


odd_indexes <- seq(1,nrow(estimates), 2)

even_indexes <- seq(2,nrow(estimates),2)

estimates[odd_indexes, 1 ] <- district_names

estimates[even_indexes, 1] <- "After"

estimates$p_value = format(estimates$p_value , scientific = FALSE)

after_coef = estimates[even_indexes, ]
after_coef$District <- district_names

# Specify the width of your confidence intervals
interval1 <- -qnorm((1 - 0.9)/2)  # 90% multiplier
interval2 <- -qnorm((1 - 0.95)/2)  # 95% multiplier
```

```{r}
print(xtable(after_coef), include.rownames = FALSE)
```


```{r echo=FALSE}
pd = colSums(Larceny) 
df = data.frame(pd)
df = setDT(df, keep.rownames = TRUE)[]

total = sum(df$pd)

df = mutate(df, Percentage = (pd/total) * 100)
df[, 1 ] <- district_names
colnames(df) = c("District","Count", "Percentage")
df$Percentage = round(df$Percentage, digits = 2)
```

```{r}
xtable(df)
```




